%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
% Based on Awesome CV LaTeX Template for Cover Letter
% from Claud D. Park <posquit0.bj@gmail.com>
% Downloaded from: https://github.com/posquit0/Awesome-CV
%
% Author: Ramiro Vignolo
% https://github.com/rvignolo/cv
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{templates/awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-nephritis}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{profile}
\name{Ramiro}{Vignolo}
\position{Nuclear Engineer {\enskip\cdotp\enskip} Lead Quantitative Analyst \& Developer}
\address{Aguilar 2275, Palermo, Buenos Aires, Argentina}

\mobile{(+54) 9 11 6482-4868}
\email{ramirovignolo@gmail.com}
% \homepage{page-url}
\github{rvignolo}
\linkedin{rvignolo}
% \gitlab{gitlab-id}
\stackoverflow{49886}{rvignolo}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Seaborg Technologies\\Titangade 11\\2200 Copenhagen N, Denmark}

% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Nuclear Engineer}
% How the letter is opened
\letteropening{Dear Sir / Madam}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
\lfooter{\today}
\cfooter{R. Vignolo~~~·~~~Cover Letter}
\rfooter{\thepage/\pageref{LastPage}}
% Leave any of these blank if they are not needed
\makecvfooter

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

I am writing this letter to apply for a 'Nuclear Engineer' position within Seaborg
Technologies. I strongly feel that my qualifications and experience make me a resourceful
candidate for a disruptive and forward-thinking company such as Seaborg.

As you can see in my attached CV, I am a Nuclear Engineer with more than seven years of
experience in mathematical modeling, numerical simulation, and programming for solving
scientific problems in a wide variety of domains, such as nuclear \& reactor physics, heat
transfer, and quantitative finance.

Regarding my education, I obtained my degree from the Balseiro Institute, a unique school in
Argentina that is known for its high-quality education. On the other hand, I am regularly
learning new technologies as well as perfecting my capabilities. I enjoy learning new things
and teaching what I have already understood.

Since I finished my University studies, I started working for the Nuclear Industry building
software for reactor physics and heat transfer applications. I believe a great way to
understand the underlying mechanisms in detail is by developing such complex computational
tools, which aid operators and designers of nuclear power plants to fulfill their daily
tasks. TECNA, the first company where I worked as a Nuclear Engineer, was mainly focused on
the Oil \& Gas Industry. However, there was a Nuclear Engineering Department formed by three
colleagues and me. Even though we were a small team, we had important contracts within the
industry that translated to a lot of responsibilities from the beginning of my career. These
contracts were focused on developing many computational libraries for Atucha I, Atucha II,
and Embalse Nuclear Power Plants. In BESNA, the second company where I worked as a Nuclear
Engineer, I developed a two-phase flow computational tool for the helically coiled steam
generators of the CAREM25 Nuclear Power Plant.

At the beginning of 2018, I decided to shift to a different domain because of the context of
the Nuclear Sector in my country. I started working as a Quantitative Analyst in the
Financial Industry, which has many points in common with what I was previously doing:
building computational libraries for solving complex scientific problems. This is an example
that gives an idea of my character, showing that I was capable of adapting to new challenges
and become proficient in new domains if needed.

Even though I made this career change, I kept building open source software for nuclear
applications because it is my true passion. There are many examples in my GitHub
repositories, including ray tracing algorithms, neutron transport approximations, or
two-phase flow computations.

I am fully aware that the current 'Nuclear Engineer' open position does not completely match
my background. But I would love to have a chance to work with you if there is an opening for
a Nuclear Engineer with similar credentials to mine. I am passionate, and I think of myself
as a kind person that is always open to feedback. Also, another important reason why I am
considering working at Seaborg is to have the opportunity to live in such a beautiful
country working with international colleagues.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}